\LARGE Untangling the link between traits, size and growth rate in plants

### 2016-07-28 figure_conceptual.tex
Add missing panels from conceptual figure

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}b}{\textrm{d}t}$}{output/con/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{$y$}{output/con/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{output/con/net_mass_production_dt_assimilation}{-}
\othercol{4}{\ $R$}{output/con/net_mass_production_dt_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{output/con/net_mass_production_dt_turnover}{}
\rowlabel{(1)}

@@

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_stem_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{output/con/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_leaf_dt}{+}
\othercol{4}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_heartwood_dt}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{output/con/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{\sqrt{\pi}}{\sqrt{a_{\textrm{st}}}}$}{output/con/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/con/diameter_stem_dt_area_stem_dt}{}
\rowlabel{(6)}

>>>>

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}b}{\textrm{d}t}$}{output/con/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{$\alpha_y$}{output/con/net_mass_production_dt_yield}{$\times$}
\othercol{3}{$\Bigg(\textrm{P}$}{output/con/net_mass_production_dt_assimilation}{-}
\othercol{4}{\ $\textrm{R}$}{output/con/net_mass_production_dt_respiration}{$\Bigg)$}
\othercol{5}{$-\textrm{T}$}{output/con/net_mass_production_dt_turnover}{}
\rowlabel{(1)}

@@

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{output/con/area_stem_dt_darea_sapwood_darea_leaf}{$+$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{output/con/area_stem_dt_darea_bark_darea_leaf}{$\Bigg)$}
\othercol{4}{\hspace{-0.2em}$\times\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{output/con/area_stem_dt_area_heartwood_dt}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{output/con/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{D}{\textrm{d}a_{\textrm{st}}}$}{output/con/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/con/diameter_stem_dt_area_stem_dt}{}
\rowlabel{(6)}
